---
title: "Task 3"
author: "Kseniia Vii"
date: "11/19/2024"
format: html
editor: visual
---

## Inroduction

In this task, we are exploring the `airquality.csv` dataset.

Read the dataset Load necessary library

```{r}
df <- airquality
```

1.  What are the column names of the data frame?

```{r}
colnames(df)
```

2.  What are the row names of the data frame?

```{r}
rownames(airquality)
```

3.  Extract the first 6 rows of the data frame and print them to the console

```{r}
head(airquality, 6)
```

4.  How many observations (i.e. rows) are in this data frame?

```{r}
nrow(airquality)
```

5.  Extract the last 6 rows of the data frame and print them to the console

```{r}
tail(airquality, 6)
```

6.  How many missing values are in the "Ozone" column of this data frame?

```{r}
sum(is.na(airquality$Ozone))
```

7.  What is the mean of the "Ozone" column in this dataset? Exclude missing values (coded as NA) from this calculation.

```{r}
mean(airquality$Ozone, na.rm = TRUE)
```

8.  Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90.

```{r}
library(dplyr)
subset_airquality <- airquality |> 
  filter(Ozone > 31 & Temp > 90)

print(subset_airquality)
```
